### 2020-03-05 short.body.tex
i like this explanation

Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ from 0.5 to 1.5, one at a time, and infer $q$ as well as ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (thus, faster infection) drive transmission events during the growth phase.
On the other hand, assuming a wider asymptomatic generation interval (higher $\kappa_a$) increases $q$ because

Figure~\ref{fig.relevance}C shows that
when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
with $q$. 
This increase arises because asymptomatic infections that resolve
slower increase the duration of
overall generation intervals (see~\citep{park_2019practical}). In contrast,
Figure~\ref{fig.relevance}D show that
when $\gamma_a>\gamma_s$ then
the strength ${\cal{R}}_0$ decreases with $q$.  
This decrease arises because asymptomatic infections that resolve
faster decrease the duration of
overall generation intervals (again, see~\citep{park_2019practical}). In both 
cases, the dependence of ${\cal{R}}_0$ on $q$ is
compared to a baseline of 
${\cal{R}}_0\approx 3.1$ in a model with no secondary
case production from asymptomatic infections (see filled
circle at bottom left of Figure~\ref{fig.relevance}C-D.
In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.

>>>>

Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ from 0.5 to 1.5, one at a time, and infer $q$ as well as ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) drive transmission events during the growth phase.
On the other hand, assuming a wider asymptomatic generation interval (higher $\kappa_a$) increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission) increases.

%Figure~\ref{fig.relevance}C shows that
%when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
%with $q$. 
%This increase arises because asymptomatic infections that resolve
%slower increase the duration of
%overall generation intervals (see~\citep{park_2019practical}). In contrast,
%Figure~\ref{fig.relevance}D show that
%when $\gamma_a>\gamma_s$ then
%the strength ${\cal{R}}_0$ decreases with $q$.  
%This decrease arises because asymptomatic infections that resolve
%faster decrease the duration of
%overall generation intervals (again, see~\citep{park_2019practical}). In both 
%cases, the dependence of ${\cal{R}}_0$ on $q$ is
%compared to a baseline of 
%${\cal{R}}_0\approx 3.1$ in a model with no secondary
%case production from asymptomatic infections (see filled
%circle at bottom left of Figure~\ref{fig.relevance}C-D.
%In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
